\emph{Light Exposure Behavior Assessment (LEBA)}: Develop of a novel instrument to capture light exposure-related behaviours

### 2021-08-27 manuscript.Rmd
updated on August 27 10PM

# Confirmatory Factor Analysis

```{r CFA, }
LB.cfa <- read_excel("SpitschanSleepSurvey_DATA_2021-08-24_1819_redacted_199_CFA.xlsx")
LB.cfa$id <- NULL
summarize <- summary(LB.cfa)
Descriptives <- psych::describe(LB.cfa)
#Univariate Normality
normality <- normality(LB.cfa) 
#Multivariate Normality
mardia(LB.cfa, na.rm = T, plot =F)

# CFA with five factor (23 items)
LB.model.Cor <- "F1 =~ item31+ item33+ item1+ item37 + item 24
             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item 7 + item11 + item42 + item12 + item16 
            F5 =~ item19 + item34 + item2" 
fit.Cor <- cfa(LB.model.Cor, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
## Summary of Model 
summary(fit.Cor, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
## Selected Fit measures 
fitmeasures (fit.Cor,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))

@@

Based on CFI, TLI, RMSEA and SRMR value the fitted five factor model is not acceptable.
As a result a close inspection  on items with low factor-loadings and low R-square value was conducted. two items were found to be problematic **item7, item 24** with vary low R-square 
value thus discarded from the model.

```{r CFA23}
#Five factor correlational Model without item24, item 7 [21 Items]
LB.model.Cor.2 <- "F1 =~ item31+ item33+ item1+ item37
             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
            F3 =~ item43 + item26 + item32
           F4 =~  item14 +  item42 + item12 + item11 + item16 
             F5 =~ item19 + item34 + item2" 
## Fit the model 
fit.Cor.2 <- cfa(LB.model.Cor.2, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
## Summary of Model 
summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
## Selected Fit measures 
fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))
rownames <-  ("fitIndices")
colnames <- c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic")
dimnames <- list(rownames, colnames)
fitmatrix <- matrix(fit.2, nrow = 1, ncol = 9, byrow = T, dimnames)
semTools::reliability(fit.Cor.2)
```

```{r CFA5Mod}
modfit.Cor <- modindices(fit.Cor.2, sort. = TRUE) 
modfit.Cor[modfit.Cor$mi>3.84,] 
```

```{r CFA5bestfit}
#21 items
LB.model.Cor.3 <- "F1 =~ item31+ item33+ item1+ item37
             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
            F3 =~ item43 + item26 + item32
           F4 =~  item14 +  item42 + item12 + item11 + item16 
             F5 =~ item19 + item34 + item2
                    item31 ~~ item33
                     item12 ~~ item11" 
## Fit the model 
fit.Cor.3 <- cfa(LB.model.Cor.3, data = LB.cfa, estimator = "MLR", mimic = "Mplus") 
## Summary of Model 
summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)
## Selected Fit measures 
fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))
rownames <-  ("fitIndices")
colnames <- c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic")
dimnames <- list(rownames, colnames)
fitmatrix <- matrix(fit.3, nrow = 1, ncol = 9, byrow = T, dimnames)
reliability1 <- semTools::reliability(fit.Cor.3, return.total = T)
as.table(reliability1 )
```

```{r CFA6}
#24 items
LB.model.Cor.4 <- "F1 =~ item31+ item33+ item1+ item37
             F2 =~ item10 + item47 + item36 +  item35 + item13 + item44
            F3 =~ item43 + item26 + item32
           F4 =~  item14 +  item42 + item12 + item11 + item16 
             F5 =~ item19 + item34 + item2
             F6 =~ item38 + item28 + item45
                   item31 ~~ item33
                    item10 ~~ item13
                     item12 ~~ item11
                     item26 ~~ item19  "

## Fit the model 
fit.Cor.4 <- cfa(LB.model.Cor.4, data = LB.cfa, estimator = "MLR", mimic = "Mplus")

## Summary of Model 
summary(fit.Cor.4, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.4 <- fitmeasures (fit.Cor.4,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))
reliability <- semTools::reliability(fit.Cor.4, return.total = T)
as.table(reliability)
```

@@

\newpage

# References

>>>>

# Confirmatory Factor Analysis
# Confirmatory Factor Analysis

```{r CFA 23 items, include=FALSE}
LB.cfa <- read_excel("recoded not reversed_CFA.xlsx")
LB.model.Cor <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item41+ item7 + item27 + item21
            F5 =~ item19 + item34 + item2"

fit.Cor <- cfa(LB.model.Cor, data = LB.cfa, estimator = "MLR", mimic = "Mplus")

## Summary of Model 
summary(fit.Cor, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.1 <- fitmeasures (fit.Cor,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))

@@

```{r CFA23withMI, include=FALSE}
LB.model.Cor.3 <- "F1 =~ item5 + item24 + item30 + item1 + item16 + item28
             F2 =~ item10 + item47 + item36 + item44 + item35 + item13
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item41+ item7 + item27 + item21
            F5 =~ item19 + item34 + item2
item44 ~~ item13
item14 ~~  item7
item10 ~~ item13"

## Fit the model 
fit.Cor.3 <- cfa(LB.model.Cor.3, data = LB.cfa, estimator = "MLR", mimic = "Mplus")

reliability <- semTools::reliability(fit.Cor.3, return.total = T)
as.table(reliability)
## Summary of Model 
summary(fit.Cor.3, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.3 <- fitmeasures (fit.Cor.3,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))

rownames <-  ("fitIndices")
colnames <- c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic")

```{r CFI18items, include=FALSE}
LB.model.Cor.2 <- "F1 =~ item5 + item24 + item30 + item16 
             F2 =~ item10 + item47 + item36 + item44 + item35 
            F3 =~ item43 + item26 + item32
           F4 =~  item14 + item41+ item7 
            F5 =~ item19 + item34 + item2
item14 ~~  item7"

#item 1 &28 discarded from F1;
#item13 discarded from F2
#item 27 & 21 discarded from F4

## Fit the model 
fit.Cor.2 <- cfa(LB.model.Cor.2, data = LB.cfa, estimator = "MLR", mimic = "Mplus")

## Summary of Model 
summary(fit.Cor.2, fit.measures =TRUE,standardized = TRUE, rsq =TRUE)

## Selected Fit measures 
fit.2 <- fitmeasures (fit.Cor.2,c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic"))

rownames <-  ("fitIndices")
colnames <- c("gfi", "agfi", "nfi","rfi", 
                       "cfi.robust","tli.robust",
                       "rmsea.robust", 
                       "srmr","aic")

@@

\newpage
# References
